\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-03 paper/main.tex
rewrote introduction, added shareable code figure

\title{\texttt{davos}: The Python package smuggler}
\author{Paxton C. Fitzpatrick}
\author{Jeremy R. Manning\corref{cor}}
\ead{Jeremy.R.Manning@Dartmouth.edu}
\cortext[cor]{Corresponding author}
\address{Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755}

@@

\begin{abstract}
% 100-word limit (though many published articles don't seem to conform to this?)

TODO: clean up after writing body

Reproducible code plays many important roles in modern scientific research: it enables scientists to collaborate on projects,\comment{parallelize data collection across multiple sites or machines} replicate and extend prior work, and teach students new concepts and techniques via hands-on, interactive tutorials.
However, existing tools that facilitate creating, sharing, and running reproducible code are often highly complex and resource-intensive, creating barriers to both contributing to and benefitting from open science resources.
Here, we introduce \texttt{davos}, a Python package that allows users to create and share reproducible workflows...

@@

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version &  v0.1.1 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.1.1} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, Ipykernel, PyZMQ. Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & Dependencies:~Python$>$=3.6, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors. \\
\hline
C8 & If available Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & contextualdynamics@gmail.com \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}

@@

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}
Modern scientific research frequently entails writing software code for a wide variety of purposes throughout the scientific process.
Researchers across disciplines may design and implement complex experiments; collect, store, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
However, one fundamental requirement of virtually any form of research-related code is that its behavior and outputs remain consistent and predictable, no matter when, where, or by whom it is run.
This stability can be crucial, for example, to ensuring that data are collected under the same conditions (e.g., across recordings, subjects, or physical locations)
%^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
over multiple months or years, and that they can be accessed, processed, and analyzed consistently by a research team that may be spread across multiple institutions or countries.
Additionally, modern open science practices encourage publicly sharing research code and data so that others may explore, reproduce, learn from, and build upon existing work.
Much of the benefit afforded by freely available research code depends on users' ability to execute it and achieve the same result as its original author.

>>>>

\title{\texttt{davos}: a Python package ``smuggler'' for constructing
  lightweight reproducible notebooks}
\author{Paxton C. Fitzpatrick}
\author{Jeremy R. Manning\corref{cor}}
\ead{Jeremy.R.Manning@Dartmouth.edu}
\cortext[cor]{Corresponding author}
\address{Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755}

@@

\begin{abstract}
% 100-word limit (though many published articles don't seem to conform
% to this?)

A core requirement of modern scientific research is replicability.
For computational research, replicability means that code should
produce the same results, even when run on different systems.  The
standard solution to improving replicability entails packaging a
project's dependencies along with its primary code base.  Existing
solutions vary in how deeply these dependencies are specified, ranging
from virtual environments (which specify all Python package versions),
to containers (which also specify the operating system), to
virtual machines (which also specify hardware layers of the system).
Each of these existing solutions requires installing or setting up a
system for running the desired code that must be packaged alongside
the primary code base.  Here we propose an even lighter-weight
solution than virtual environments: the \texttt{davos} library.  When
used in combination with a notebook-based Python project, \texttt{davos}
library provides a mechanism for specifying (and automatically
installing) the correct package versions of the project's.  This
enables researchers to share a complete reproducible environment using
a single iPython notebook file.

@@

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Notes} \\
\hline
C1 & Current code version &  v0.1.1 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.1.1} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, Ipykernel, PyZMQ. Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & Dependencies:~Python$>$=3.6, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors. \\
\hline
C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & contextualdynamics@gmail.com \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}

@@

% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
\section{Motivation and significance}

Jupyter (iPython) notebooks~\citep{KluyEtal16} have revolutionized
code sharing by providing a single filetype that combines text, code,
and figures.  For projects that depend on other software packages,
however, additional work is often required to enable the code to run
as its authors intended.  For example, a piece of software that
depends on version 0.8 of package \textit{X} may behave differently
(or may fail to run at all) if the user instead attempts to run the
code in an environment with version 0.9 of package \textit{X}.

% STOPPED HERE...

Sharing a project's code base is most valuable when that code may be
run on

Modern scientific research frequently entails writing software code
for a wide variety of purposes throughout the scientific process.
Researchers across disciplines may design and implement complex
experiments; collect, store, and analyze large datasets; create
visualizations for presentations and publications; and share their
findings and techniques with peers, students, and the broader public
through tutorials, demos, workshops, and classes.  However, one
fundamental requirement of virtually any form of research-related code
is that its behavior and outputs remain consistent and predictable, no
matter when, where, or by whom it is run.  This stability can be
crucial, for example, to ensuring that data are collected under the
same conditions (e.g., across recordings, subjects, or physical
locations)
%^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
over multiple months or years, and that they can be accessed,
processed, and analyzed consistently by a research team that may be
spread across multiple institutions or countries.  Additionally,
modern open science practices encourage publicly sharing research code
and data so that others may explore, reproduce, learn from, and build
upon existing work.  Much of the benefit afforded by freely available
research code depends on users' ability to execute it and achieve the
same result as its original author.
